### 2016-10-26 JournalTorqueControl/theory.tex
changed captions

@@

%pivoted comparisons:
\begin{figure*}
\centering
\renewcommand{\figwid}{\columnwidth}
\begin{overpic}[width =\figwid]{BestLocationPivot.pdf}%\put(1,55){a)}
\end{overpic}
\begin{overpic}[width =\figwid]{MaxTorquePivot.pdf}%\put(1,55){a)}
\end{overpic}
\vspace{-0.5em}
\caption{\label{fig:bestLoc} Best location to push in two different situations: when the object is pivoted, and when the object is free.
%\vspace{-2em}
}
\end{figure*}

\begin{figure*}
\centering
\renewcommand{\figwid}{\columnwidth}
\begin{overpic}[width =\figwid]{TorqueFreeBestPush.pdf}
\end{overpic}
\begin{overpic}[width =\figwid]{TorqueFreeComparison.pdf}
\end{overpic}
\vspace{-0.5em}
\caption{\label{fig:maxTorque} Maximum torque possible in two situations: pivoted object and free object.
%\vspace{-2em}
}
\end{figure*}

>>>>

%pivoted comparisons:
\begin{figure*}
\centering
\renewcommand{\figwid}{\columnwidth}
\begin{overpic}[width =\figwid]{BestLocationPivot.pdf}%\put(1,55){a)}
\end{overpic}
\begin{overpic}[width =\figwid]{MaxTorquePivot.pdf}%\put(1,55){a)}
\end{overpic}
\vspace{-0.5em}
\caption{\label{fig:bestLoc} Best location to push and maximum torque plot in pivoted object.
%\vspace{-2em}
}
\end{figure*}

@@

%free torque comparison
\begin{figure*}
\centering
\renewcommand{\figwid}{\columnwidth}
\begin{overpic}[width =\figwid]{TorqueFreeBestPush.pdf}
\end{overpic}
\begin{overpic}[width =\figwid]{TorqueFreeComparison.pdf}
\end{overpic}
\vspace{-0.5em}
\caption{\label{fig:maxTorque} Best location to push and maximum torque plot in free object.
%\vspace{-2em}
}
\end{figure*}
